Commit Rater

### 2015-08-26 presentations/paper/abstract.tex

\begin{abstract}
  In 2014, the Git surpassed Subversion as the top code management tool
  \cite{EComSurv14}. With so many authors colaborating comes the need for a
  appropriate and standardized use of elemental actions like doing commits.
  Although the official Git documentation states very clear guidelines
  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
  simply ignore them.

  This paper presents a tool that analyzes a set of commits regarding criteria
  composed of the official guidelines and some common mistakes, and shows a
  prototypical website that encourages improvements in commit-etiquette by
  creating a competitive score-board for a given GitHub repository. We also
  perform a machine learning powered analysis of correlations between all
  criteria.
\end{abstract}

>>>>

\begin{abstract}
  In 2014, Git surpassed Subversion as the top code management tool
  \cite{EComSurv14}. With many authors collaborating comes the need for an
  appropriate and standardized use of elemental actions, like formulating
  commit messages. Although the official Git documentation states very clear
  guidelines \cite{OffGuide} on how this should be done, many users are either
  unaware or simply ignore them.

  This paper presents a tool that analyzes a set of commit messages regarding
  criteria composed of the official guidelines and some common mistakes, and
  shows a prototypical website that encourages improvements in commit message
  style by creating a competitive score-board for a given GitHub repository. We
  also perform a machine-learning-powered analysis of correlations between the
  criteria, which can help improve the selection of criteria in the future.
\end{abstract}

### 2015-08-26 presentations/paper/introduction.tex

While there has been research in the field of Mining Software Repositories about emotional content of commit messages (see section \ref{sec:related-work}), none of them have dealt with the actual quality of commits and their relation to the aformentioned best practices. In this paper, we present our approach to this topic.

We have built an application called ``Commit Rater''\footnote{\url{https://github.com/hartenfels/Commit-Rater}}, which extracts commit message data of any Git repository (see section \ref{sec:data-extraction}) and synthesizes the quantitative adherance to commit criteria (see section \ref{sec:data-synthesis}). For the sake of easy use and graphical visualization of the ratings, we have also built a web application\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}} around the tool, which, at the time of writing, is available for public use at \url{http://trollarena.de:8080/}.

>>>>

While there has been research in the field of Mining Software Repositories about emotional content of commit messages (see section \ref{sec:related-work}), none of them have dealt with the actual quality of commits and their relation to the aforementioned best practices. In this paper, we present our approach to this topic.

We have built an application called ``Commit Rater''\footnote{\url{https://github.com/hartenfels/Commit-Rater}}, which extracts commit message data of any Git repository (see section \ref{sec:data-extraction}) and synthesizes the quantitative adherence to commit criteria (see section \ref{sec:data-synthesis}). For the sake of easy use and graphical visualization of the ratings, we have also built a web application\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}} around the tool, which, at the time of writing, is available for public use at \url{http://trollarena.de:8080/}.

### 2015-08-26 presentations/paper/research_question.tex

Our research and development regarding the Commit Rater was lead by the goal of providing useful data to developers, such as ourselves, regarding their commits to help them learn and improve. The following two research questions (RQs) emerged from this objective.

>>>>

Our research and development regarding the Commit Rater was lead by the goal of providing useful data to developers, such as ourselves, regarding their commits, to help them learn and improve. The following two research questions (RQs) emerged from this objective.
